Understanding Factors Contributing to a Successful Himalayan Expedition

### 2024-04-19 other/datasheet/datasheet.qmd
Dataset related links and citations added

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was obtained by cleaning the dataset's provided by Alex Cookson: (link). Their datasets were derived from The Himalayan Database (link). The Himalayan Database is a compilation of records for all expeditions that have climbed in the Nepal Himalaya. The database is based on the expedition archives of Elizabeth Hawley, a longtime journalist based in Kathmandu, and it is supplemented by information gathered from books, alpine journals and correspondence with Himalayan climbers.

2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The csv files provided by Alex Cookson (link) were downloaded and processed. The cleaning and processing involved natural joining the three datasets and cleaning them to satisfy the analysis needs.

>>>>

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was obtained by cleaning the dataset's provided on Github by @Cookson. Their datasets were derived from The Himalayan Database. The Himalayan Database is a compilation of records for all expeditions that have climbed in the Nepal Himalaya. The database is based on the expedition archives of Elizabeth Hawley, a longtime journalist based in Kathmandu, and it is supplemented by information gathered from books, alpine journals and correspondence with Himalayan climbers.

2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The csv files provided by @Cookson were downloaded and processed. The cleaning and processing involved natural joining the three datasets and cleaning them to satisfy the analysis needs.

### 2024-04-19 paper/paper.qmd
Dataset related links and citations added

I use data from Alex Cookson’s datasets (link) which are sourced from The Himalayan Expedition records (link), to understand these factors and trends. This is done by leveraging a Bayesian Logistic Regression model and then predicting the probability of a successful attempt over various demographic and environmental factors.

@@

## Analysis Dataset
The raw datasets were obtained from Alex Cookson's datasets (link). I chose the ones cleaned for Himalayan expeditions. Alex got his datasets from The Himalayan Database (link).

@@

My dataset derived from Alex's contains the entries from 1905 through Spring 2019.

>>>>

I use data from @Cookson which are sourced from The Himalayan Expedition records (@Salisbury), to understand these factors and trends. This is done by leveraging a Bayesian Logistic Regression model and then predicting the probability of a successful attempt over various demographic and environmental factors.

@@

## Analysis Dataset
The raw datasets were obtained from @Cookson. I chose the ones cleaned for Himalayan expeditions. Cookson got his datasets from The Himalayan Database (@Salisbury).

@@

My dataset derived from Cookson's contains the entries from 1905 through Spring 2019.
